---
title: "Monopoly Game Rules"
author: "Lauren Gamber"
date: "2026-10-03"
output: pdf_document
header-includes:
- \usepackage{textcomp} % for the Won symbol 
- \usepackage{graphicx} % Needed for the rotation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

notation for monopoly money: $\rotatebox[origin=c]{180}{\textwon}$ from stack exchange post


## Game Rules 

In Monopoly, players move around the board buying and building on properties to collect more rent and become the wealthiest player. The game ends when all but one player has gone bankrupt. To set up the game, one player is assigned as the banker, the banker is responsible for the bank's money, houses, hotels, title deed cards, and auctions. The banker is permitted to be a player as well. The banker gives each player a starting wealth of \rotatebox[origin=c]{180}{\textwon} 1500 (5 x \rotatebox[origin=c]{180}{\textwon} 1, 5 x \rotatebox[origin=c]{180}{\textwon} 5, 4 x \rotatebox[origin=c]{180}{\textwon} 10, 4 x \rotatebox[origin=c]{180}{\textwon} 20, 3 x \rotatebox[origin=c]{180}{\textwon} 50, 2 x \rotatebox[origin=c]{180}{\textwon} 100, 2 x \rotatebox[origin=c]{180}{\textwon} 500 ). Each player choose a token that 


Figure ##, shows the layout of the board. On the board, there are 



```{r}


```



